Comparing belief in free will and job satisfaction in the US and Taiwan 

### 2024-02-14 paper/paper.qmd
test

Data from Study 1 were used to show the relative amount of belief in free will of the average Taiwanese real estate agents and how much are they satisfied with their job across two times within 6 months with the same sample.
We extracted the responses from the survey and extracted the responses to the questions : "From the scale of 0 to 10, How much do you agree with this statement: I have free will"and "From the scale of 0 to 10, How much do you agree with this statement: I am satisfied with my job" at Time one and two.
In Figure 1, we calculated and showed the means and standard deviation of the job satisfaction both times and belief in free will values.
response patterns along a consistent y-axis.
Dancygier et al. (2021) provides groupings for the varying elements that we wanted to distinguish and
compare. The three age/gender groups compared are: (1) All (men and women of all ages), (2) Men
between ages of 18-44, and (3) Men of “mating age” (30-40), making them of an age that is most commonly
seen as the range that people seek to find a partner and “settle down.” There were also 3 different groupings
for categorizing a municipality’s gender ratio which are referred to as “terciles.” Gender ratio was calculated
by dividing the male population by the female population of a given municipality (Dancygier et al. 2021).
Within the survey data, each response had a value for that respondents’ municipality’s gender ratio. Table 1
shows the exact value of ratio used to divide groupings into 1st, 2nd, and 3rd terciles.
Returning to Figure 1, we immediately notice that the highest rate of perceiving refugees as threats, over
46%, is found in mating-aged men living in municipalities with relatively high male-to-female ratio (at least
1.12 men per 1 woman). Next is Men ages 18-44 in the same tercile of municipalities at around 37%. This is
in stark contrast to the All group which includes men and women of all ages, where the proportion is lowest
in the 1st tercile at around 17%, and highest at the 3rd tercile with 23%. There is one exception of Men
30-40 in the 1st tercile, but otherwise, Men are consistently more likely to perceive refugees as threats to
mating than the general population. This jumps greatly the higher the male-to-female ratio is in their own
town; the rate in Men 30-40 is almost tripled in the 3rd tercile than the 1st, and about 1.8 times more than
the 2nd.
In analyzing Figure 1, we can recognize that the combination of a person being a man, especially between the
ages of 30-40, and living in a municipality that has about 9 men per 8 women does seem to predict a higher
rate of that person believing that refugees are negatively affecting their chance at finding a romantic partner.
To confirm, it is not necessarily true that these respondents are living in an area with disproportionately
more refugee men, but men in general. Yet, there being more men at all in their town might lead them to
project blame onto refugees when presented with a question regarding the topic.

>>>>

Data from Study 1 were used to show the relative amount of belief in free will of the average Taiwanese real estate agents and how much are they satisfied with their job across two times within 6 months with the same sample.
We extracted the responses from the survey and extracted the responses to the questions : "From the scale of 0 to 10, How much do you agree with this statement: I have free will"and "From the scale of 0 to 10, How much do you agree with this statement: I am satisfied with my job" at Time one and two.
In Figure 1, we calculated and showed the means and standard deviation of the job satisfaction both times and belief in free will values.
